Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-26 doc/PRF2022/PRF_main.tex
updates

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.27\textheight]{Nb198a.pdf}
  \includegraphics[height=0.27\textheight]{Nb198b_eta.pdf}\\
  \hspace{1.55cm}
  \includegraphics[height=0.27\textheight]{Nb198c_eta.pdf}
  \includegraphics[height=0.27\textheight]{Nb198d_eta_1.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles selc-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.}
\end{caption}
\end{figure}

@@

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.
\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
\includegraphics[width=0.49\textwidth]{relax_E.pdf}
\includegraphics[width=0.49\textwidth]{relax_LOP.pdf}  \\
  \includegraphics[height=0.15\textheight]{Nb60a.pdf}
  \includegraphics[height=0.15\textheight]{Nb60b.pdf}
  \includegraphics[height=0.15\textheight]{Nb60c.pdf}
 \includegraphics[height=0.15\textheight]{Nb60d.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
    The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles.
  }
\end{figure}

@@

>>>>

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
  \hspace{1.55cm}
  \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.27\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles selc-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.}
\end{caption}
\end{figure}

@@

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.

%\begin{figure}
%  \begin{center}
%  \includegraphics[height=0.15\textheight]{Nb60a.pdf}
%  \includegraphics[height=0.15\textheight]{Nb60b.pdf}
%  \includegraphics[height=0.15\textheight]{Nb60c.pdf}
% \includegraphics[height=0.15\textheight]{Nb60d.pdf}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:relax_Nb60} 
%  }
%\end{figure}

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
\includegraphics[width=0.49\textwidth]{relax_E.pdf}
\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. The near-equilibrium configurations depend on the initial configuration and the results show that 
    the striated configurations have largest value of order parameter for both $N_b=60$ and $N_b=198$ cases.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Area}
  \includegraphics[width=0.4\textwidth]{VTG_Len}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_Scale_3.pdf}
      \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
